Databrary: A digital data library for sharing research video

### 2015-01-16 jcdl-15/paper.tex
a few tiny edits
didn't get very far past first paragraph

Video plays a key role in many areas of human research, particularly in developmental psychology, education, ...
Unfortunately, in standard practice, due largely to the perceived burdens of ethics and privacy restrictions, the use of these data is isolated to the researchers who collected them.
The goal of the Databrary project establish policies and tools to allow video data to be documented, organized, and shared so that other researchers can discover and re-purpose existing videos for their own research interest.
Accordingly, Databrary, with developmental psychology as a use case, has created a web-based library and organizational structures to accommodate existing video data, capture contextual information necessary for re-use, and standardize across datasets without placing undue burden on data contributors.

>>>>

Video plays a key role in many areas of human research, particularly in developmental psychology, education, and is even a primary data source ...
Unfortunately, in standard practice, due largely to the perceived requirements about privacy restrictions, the use of these video data is isolated to the researchers who collected them.
The goal of the Databrary project is to establish policies and tools to allow video data to be documented, organized, and shared so that other researchers can discover and re-purpose existing videos for their own research interest.
Accordingly, Databrary, with developmental psychology as a use case, has created a web-based library and organizational structures to accommodate existing video data, capture contextual information necessary for re-use, and standardize across datasets without placing undue burden on data contributors.
